The MRChem MRA code for molecular electronic calculations. Performance and scaling properties

### 2022-02-21 main.tex
Updates from Overleaf

\begin{equation}
  F_{ij} = \langle \psi_i |{-\frac{1}{2}\nabla^2+V}| {\phi_j}\rangle
\end{equation}

In the HF case $V=V_n+J-K$, and in the Kohn Sham equations $V=V_n+J+V_{xc}$

@@

\subsubsection{Other}
In addition, the orbitals need to be orthonormalized, and combined (orbital rotation).

@@

In practice a computer cluster is required for calculations on large systems.
For example the representation of one orbital is described typically by of the order of 10-500MB of data (see section \ref{sizes}). Usually several sets of orbitals are required in the scf process (previous iteration, right hand size of equations etc.). If 1000 orbitals are described, this will often require more memory than is locally available on a compute node of a cluster. Therefore it is required to store the data in a distributed way. At the same time, the equations require to access all pair of orbitals, i.e. all the data must at some point be accessible locally.

@@

\subsection{Adaptivity and implicit screening}
%explanation of implicit screening mechanisms within MRA? 
% i.e. MRCPP tree calculation using norm threshold

@@

\subsubsection{Task manager} 
In a localized orbital approach, many of the elements of the matrix $\braket{\phi_i|{\hat O} \phi_j}$ will be small. Since the method is inherently adaptive using the MRCPP library, the small elements will be faster to compute. In order to fully exploit this feature, a dynamical distribution of tasks is required.  
In practice the matrix $\braket{\phi_i|{\hat O} \phi_j}$ is partitioned into blocks. Each block represent one task to be performed by a "worker". When a "worker" is done with one task it can ask for a new task from the "task manager" until all the tasks are finished.

@@

\subsection{Implicit screening}
%example of histogram of timing for each exchange terms? many terms very fast, few slow.
%example of histogram of timing for orbital rotation?

@@

BigDFT method
https://aip-scitation-org.mime.uit.no/doi/full/10.1063/1.2949547

@@

>>>>

\begin{equation}
  F_{ij} = \langle \psi_i |{-\frac{1}{2}\nabla^2+V}| {\psi_j}\rangle
\end{equation}

In the HF case $V=V_{nuc}+J-K$, and in the Kohn Sham equations $V=V_n+J+V_{xc}$, where $V_{nuc}$, $J$, $K$ , $V_{xc}$ are the nuclear, Coulomb, Exchange and exchange-correlation potentials respectively. $F$ is the Fock matrix and $-\frac{1}{2}\nabla^2 = T$ is the kinetic operator.

@@

@@

In practice a computer cluster is required for calculations on large systems.
For example the representation of one orbital is described typically by of the order of 10-500MB of data (see section \ref{sizes}). Usually several sets of orbitals are required in the scf process (previous iteration, right hand size of equations etc.). If 1000 orbitals are described, this will often require more memory than is locally available on a compute node of a cluster. Therefore it is required to store the data in a distributed way. At the same time, the equations require to access all pairs of orbitals, i.e. all the data must at some point be accessible locally.

@@

\subsection{Adaptivity}
%explanation of implicit screening mechanisms within MRA? 
% i.e. MRCPP tree calculation using norm threshold

@@

\subsubsection{Task manager} 
In a localized orbital approach, many of the elements of the matrix $\braket{\phi_i|{\hat O} \phi_j}$ will be small. Since the method is inherently adaptive using the MRCPP library, the small elements will be faster to compute. In order to fully exploit this feature, a dynamical distribution of tasks is required.  
In practice the matrix $\braket{\phi_i|{\hat O} \phi_j}$ is partitioned into blocks. Each block represent one task to be performed by a "worker". In a local representation, each node is simply one task. When a "worker" is done with one task it can ask for a new task from the "task manager" until all the tasks are finished.

@@

\subsection{Implicit screening}
%example of histogram of timing for each exchange terms? many terms very fast, few slow.
%example of histogram of timing for orbital rotation?
%could also show how much time is used for matrix mult compared to transfer time

@@

@@

%https://pubs.rsc.org/en/journals/journalissues/cp#!issueid=cp017047&type=current&issnprint=1463-9076
